An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-08 ex3/paper/paper.tex
Updated figures

\begin{table*}
\caption{Attack success ratios per attack family. Depicted are flow detection accuracies for adversarial flows (left numbers) and flow detection accuracies for unmodified flows (right numbers).}
\label{tab:adv_per_family}
\centering
\begin{tabular}{llllllllll}
\toprule
Attack type & \multicolumn{2}{l}{FGSM} & \multicolumn{2}{l}{Carlini-Wagner, $\ell_1$} & \multicolumn{2}{l}{Carlini-Wagner, $\ell_2$} & \multicolumn{2}{l}{$\ell_\infty$-bounded \gls{pgd}} \\
\cmidrule(r){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7} \cmidrule(l){8-9}
& adv. & orig. & adv. & orig. & adv. & orig. & adv. & orig. \\
\midrule
Botnet:ARES	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	\\
Brute Force:FTP-Patator	&	0.2800 & 0.5800	&	0.1600 & 0.5800	&	0.1600 & 0.5800	&	0.2800 & 0.5800	\\
Brute Force:SSH-Patator	&	0.8300 & 1.0000	&	0.0000 & 1.0000	&	0.0000 & 1.0000	&	0.8900 & 1.0000	\\
DDoS:LOIT	&	0.8300 & 0.8600	&	0.6400 & 0.8600	&	0.5600 & 0.8600	&	0.8200 & 0.8600	\\
DoS / DDoS:DoS GoldenEye	&	0.8900 & 1.0000	&	0.5000 & 1.0000	&	0.4200 & 1.0000	&	0.9200 & 1.0000	\\
DoS / DDoS:DoS Hulk	&	0.6700 & 1.0000	&	0.5400 & 1.0000	&	0.4700 & 1.0000	&	1.0000 & 1.0000	\\
DoS / DDoS:DoS Slowhttptest	&	0.8700 & 1.0000	&	0.4100 & 1.0000	&	0.1900 & 1.0000	&	0.7400 & 1.0000	\\
DoS / DDoS:DoS slowloris	&	0.4400 & 0.9700	&	0.3100 & 0.9700	&	0.1300 & 0.9700	&	0.9200 & 0.9700	\\
DoS / DDoS:Heartbleed	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	\\
Infiltration:Dropbox download 	&	0.6100 & 0.9600	&	0.4300 & 0.9600	&	0.3800 & 0.9600	&	0.7400 & 0.9600	\\
PortScan:PortScan - Firewall off	&	0.6800 & 0.9100	&	0.3500 & 0.9100	&	0.3500 & 0.9100	&	0.7200 & 0.9100	\\
PortScan:PortScan - Firewall on	&	0.7400 & 0.8700	&	0.6100 & 0.8700	&	0.5300 & 0.8700	&	0.7300 & 0.8700	\\
Web Attack:Sql Injection	&	0.0000 & 0.6923	&	0.0000 & 0.6923	&	0.0000 & 0.6923	&	0.0000 & 0.6923	\\
Web Attack:XSS	&	0.6700 & 0.9500	&	0.7200 & 0.9500	&	0.6200 & 0.9500	&	0.6700 & 0.9500	\\
\bottomrule

\end{tabular}

\todo{In the adv table, round the numbers!!! \\
For Max: Introduce two-level table\\
What's the tradeoff for CW?}
\end{table*}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/adv_training/avdistance.pdf}
\caption{Distance of adversarial samples from original attack samples throughout adversarial training.}
\label{fig:avdistance}
\end{figure}

>>>>

% \begin{table*}
% \caption{Attack success ratios per attack family. Depicted are flow detection accuracies for adversarial flows (left numbers) and flow detection accuracies for unmodified flows (right numbers).}
% \label{tab:adv_per_family}
% \centering
% \begin{tabular}{llllllllll}
% \toprule
% Attack type & \multicolumn{2}{l}{FGSM} & \multicolumn{2}{l}{Carlini-Wagner, $\ell_1$} & \multicolumn{2}{l}{Carlini-Wagner, $\ell_2$} & \multicolumn{2}{l}{$\ell_\infty$-bounded \gls{pgd}} \\
% \cmidrule(r){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7} \cmidrule(l){8-9}
% & adv. & orig. & adv. & orig. & adv. & orig. & adv. & orig. \\
% \midrule
% Botnet:ARES	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	\\
% Brute Force:FTP-Patator	&	0.2800 & 0.5800	&	0.1600 & 0.5800	&	0.1600 & 0.5800	&	0.2800 & 0.5800	\\
% Brute Force:SSH-Patator	&	0.8300 & 1.0000	&	0.0000 & 1.0000	&	0.0000 & 1.0000	&	0.8900 & 1.0000	\\
% DDoS:LOIT	&	0.8300 & 0.8600	&	0.6400 & 0.8600	&	0.5600 & 0.8600	&	0.8200 & 0.8600	\\
% DoS / DDoS:DoS GoldenEye	&	0.8900 & 1.0000	&	0.5000 & 1.0000	&	0.4200 & 1.0000	&	0.9200 & 1.0000	\\
% DoS / DDoS:DoS Hulk	&	0.6700 & 1.0000	&	0.5400 & 1.0000	&	0.4700 & 1.0000	&	1.0000 & 1.0000	\\
% DoS / DDoS:DoS Slowhttptest	&	0.8700 & 1.0000	&	0.4100 & 1.0000	&	0.1900 & 1.0000	&	0.7400 & 1.0000	\\
% DoS / DDoS:DoS slowloris	&	0.4400 & 0.9700	&	0.3100 & 0.9700	&	0.1300 & 0.9700	&	0.9200 & 0.9700	\\
% DoS / DDoS:Heartbleed	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	&	0.0000 & 0.0000	\\
% Infiltration:Dropbox download 	&	0.6100 & 0.9600	&	0.4300 & 0.9600	&	0.3800 & 0.9600	&	0.7400 & 0.9600	\\
% PortScan:PortScan - Firewall off	&	0.6800 & 0.9100	&	0.3500 & 0.9100	&	0.3500 & 0.9100	&	0.7200 & 0.9100	\\
% PortScan:PortScan - Firewall on	&	0.7400 & 0.8700	&	0.6100 & 0.8700	&	0.5300 & 0.8700	&	0.7300 & 0.8700	\\
% Web Attack:Sql Injection	&	0.0000 & 0.6923	&	0.0000 & 0.6923	&	0.0000 & 0.6923	&	0.0000 & 0.6923	\\
% Web Attack:XSS	&	0.6700 & 0.9500	&	0.7200 & 0.9500	&	0.6200 & 0.9500	&	0.6700 & 0.9500	\\
% \bottomrule

% \end{tabular}

% \todo{In the adv table, round the numbers!!! \\
% For Max: Introduce two-level table\\
% What's the tradeoff for CW?}
% \end{table*}

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/adv_comparison/adv_comparison_17.pdf}
\label{fig:adv_per_family}
\caption{Attack success ratios per attack family. Depicted are flow detection accuracies for adversarial flows and for unmodified flows.}
\todo{update numbers, shorten attack names, What's the tradeoff for CW?}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/ars/ars_15.pdf}
\caption{\gls{ars} during adversarial training for UNSW-NB15.}
\label{fig:avdistance}
\end{figure}
